Explore the SingleR results

### 2025-07-15 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/singler-results.Rmd
swap in validation url and add table of cell types and labels

# marker genes for validation
consensus_markers_file <- file.path(ref_dir, "consensus-marker-genes.tsv")
nbatlas_markers_file <- file.path(ref_dir, "nbatlas-marker-genes.tsv")
```

@@

@@

We'll show the top-seven highest logFC marker genes per cell type for validation.

```{r}
# number of marker genes to consider per validation group
n_marker_genes <- 7

>>>>

# marker genes for validation
consensus_markers_file <- "https://raw.githubusercontent.com/AlexsLemonade/OpenScPCA-analysis/refs/heads/main/analyses/cell-type-consensus/references/validation-markers.tsv"
nbatlas_markers_file <- file.path(ref_dir, "nbatlas-marker-genes.tsv")
```

@@

## Cell type comparisons

Throughout this notebook, we compare the cell type labels from `SingleR` with the consensus cell type labels.
To facilitate this, the `SingleR` labels from `NBAtlas` were grouped together to both a) mirror (where possible) the broad consensus labels, and b) to make some visualizations more manageable.

The table below shows the `NBAtlas` cell types and how they are represented in visualizations, unless otherwise stated.

| Broad label shown in figures | Associated NBAtlas labels                                       |
| ---------------------------- | --------------------------------------------------------------- |
| `T cell`                     | `CD4+ T cell`, `CD8+ T cell`, `Treg`, `NKT cell`                |
| `dendritic cell`             | `cDC1`, `cDC2/DC3`, `Migratory cDC`                             |
| `natural killer cell cell`   | `Circulating NK cell`, `TOX2+/KIT+ NK cell`, `Resident NK cell` |
| `monocyte`                   | `CD4+ T cell`, `Classical monocyte`, `Patrolling monocyte`      |
| `myeloid`                    | `Neutrophil`                                                    |
| `Neuroendocrine`             | `Neuroendocrine`                                                |
| `fibroblast`                 | `Fibroblast`                                                    |
| `macrophage`                 | `Macrophage`                                                    |
| `B cell`                     | `B cell`                                                        |
| `plasma cell`                | `Plasma`                                                        |
| `endothelial`                | `Endothelial`                                                   |
| `Stromal other (NBAtlas)`    | `Stromal other`                                                 |
| `Schwann`                    | `Schwann`                                                       |
| `RBCs`                       | `RBCs`                                                          |
| `Immune cycling`             | `Immune cycling`                                                |
| `pDC`                        | `pDC`                                                           |

Cells labeled `singler_unknown` are those for which `SingleR` could not reliably assign an annotation.

@@

We'll show the top-5 highest log2FC marker genes per cell type for validation.

```{r}
# number of marker genes to consider per validation group
n_marker_genes <- 5
